---
title: "General Genetics"
subtitle: "BIOB 375"
author: "Fernando Correr"
date: "5/16/2022"
output:
  xaringan::moon_reader:
    css: ["default","./style/msu_biob.css", "./style/msu_biob_fonts.css"]
    lib_dir: libs
    nature:
      beforeInit: ["./js/MSUThememacros.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

## BIOB 375 - Summer 2022

May 16 - June 24

**Instructor**: Fernando Correr, PhD

- Department of Plant Science and Plant Pathology (204)

- email: fernando.correr@montana.edu

**Textbook**: Benjamin A. Pierce - Genetics: A Conceptual Approach (7th edition)


**Pre-requisites**: Principles of Biology (BIOB 160)  or Cellular and Molecular Biology (BIOB 260) or  BIOB 360

---
class: sec-inverse, center, middle

# Introduce yourself!


---
class: sec-inverse, center, middle

# Get Started

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```
