---
title: "General Genetics"
subtitle: "BIOB 375"
author: "Fernando Correr"
date: "5/16/2022"
runtime: shiny
output:
   ioslides_presentation:
      css: ../style/msu_biob.css
      logo: ../style/MSU-logo.png
      widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## BIOB 375

Summer 2022: May 16 - June 24

**Instructor**: Fernando Correr, PhD

- Department of Plant Science and Plant Pathology (204)

- email: fernando.correr@montana.edu

**Textbook**: Benjamin A. Pierce - Genetics: A Conceptual Approach (7th edition)


**Pre-requisites**: Principles of Biology (BIOB 160)  or Cellular and Molecular Biology (BIOB 260) or  BIOB 360


## Title {.dark}

aaaaaa

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

##

<div style="margin-left:-50px; margin-top:-50px; width:80%; height:100%">
```{r, echo=FALSE, message=FALSE, fig.width=8}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),

  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")

  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```
</div>
