---
title: "Exercises"
author: "<b>Lachowiec Lab</b> <br> Montana State University"
date: 19/10/2022
output: 
      rmdformats::readthedown:
        css: ["./style/style.css"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
## Global options
options(max.print="75")
opts_knit$set(width=75)
```


## Part 1 - Basic operations

1 - In an experiment to evaluate the value fo cultivation and use (VCU) in corn, the plots consisted of two rows of four meters, spaced 0.60 m, totaling 6 plants per row. The heights of the plants were respectively (in meters): 1.45; 1.73; 1.98; 2.10; 2.03; 1.65; 2.15; 1.63; 1.53; 1.98; 2.05; 1.52.

* Create a vector for height with the above values;

* Calculate the average height;

* Calculate the variance of the heights;

2 - In General Genetics, height and weight of 10 students were evaluated, five girls and five boys. See the table below with the respective values:

| **Name**   | **Weight (kg)** | **Height (m)** |
|------------|---------------|----------------|
| Maria José | 72            | 1.65           |
| Mariana    | 57            | 1.68           |
| Fernanda   | 49            | 1.53           |
| Jéssica    | 62            | 1.70            |
| Carolina   | 57            | 1.52           |
| Paulo      | 90            | 1.82           |
| Marcos     | 53            | 1.63           |
| João Paulo | 76            | 1.78           |
| Geraldo    | 63            | 1.72           |
| Pedro      | 92            | 1.98           |


* Calculate the Body Mass Index (BMI) of each student, according to the formula: $BMI=\frac{weight}{height^2}$

* Calculate the average BMI of the classroom.

* Calculate the variance of the BMI.

* Calculate the standard deviation of BMI.

3 - Solve the equation $2x^2 + 8x + 6 = 0$ using Bhaskara's formula. Remember: $x = \frac{-b \pm \sqrt{\Delta}}{2a}$; $\Delta = b^2 - 4ac$

## Part 2 - Objects

1 - Load the dataset named “mtcars” (`attach(mtcars)`).

* Verify the class of the object `mtcars`.

* Verify the class of the columns `hp` and `cyl`.

* Verify the class of the name of the cars (use `rownames`).


2- Using the same dataset as in the previous exercise:

* Calculate the average of the `hp` column.

* Change the column class `hp` to factor and average again.

* Compare the results obtained in the previous items, and report the differences between them.

3 - Create a list of the names of the following rock band members with their date and place of birth.

| **Name** | **Role** | **Age** |
|----------|----------|---------|
| Dinho    | Vocals   | 24      |
| Bento    | Guitar   | 25      |
| Samuel   | Bass     | 22      |
| Sérgio   | Drumms   | 26      |
| Rasec    | Keyboard | 28      |

```{r echo=FALSE, eval=FALSE}
 ##Ex 3
  list_mam <- list(Nomes= c("Dinho", "Bento", "Samuel", "Sérgio", "Rasec"),
                   Funcao=c("Vocalista","Guitarrista", "Baixista", "Baterista","Tecladista"),
                   Idade = c(24, 25, 22, 26, 28))
 l_idade <- mean(list_mam$Idade)
  l_ordered <- lapply(list_mam, function(x){ x[order(list_mam$Nomes)]})
```

* Check the length of the list.

* Using the list, calculate the mean age.

* Sort the list in alphabetical order of names.

## Part 3 - Indexes

1 - Create a vector from a sample of the Normal distribution with length of 30,000, mean 20 and standard deviation 5. Before creating the vector, use `set.seed(123456)`.

* What is the sum of observations that are greater than 30?

* What about the sum of observations smaller than the mean?

* Delete the smallest observation from the vector.

## Part 4 - Conditionals and repetition structures

1 - Create an object `a` containing a sequence from 1 to 5. Using any repeating structure, add the number 8 to each of the elements of `a`, until the sum of all elements is equal to or greater than 10000.

```{r echo=FALSE, eval=FALSE}
a = seq(1,5,1)
  while(sum(a) < 10000){
    a = a + 8
  }
```


2 - Use the expression below to generate random yield averages (kg/ha) of 50 soybean genotypes:

```{r eval=FALSE}
set.seed(123456)
produtividade = rnorm(50, mean = 3500.00, sd = 800)
```

Let's assume that the national average of soybean yield is 3500.00 kg/ha. Using conditional structures, check whether the genotypes present values above or below the national average productivity, returning the phrases `above average` or `below average`, respectively.

# Main tutorial

To return to the main tutorial click [here](R_training.html).